An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-11 EconGrowth-R-Functions.Rnw
Now including CES without energy predictions in the CES lattice graph.

#########################
# Takes the CES fitted models and creates per-country predictions for them.
# Returns a data.frame with the predictions.
##
cesPredictions <- function(countryAbbrev, energyType){
  dataTable <- loadAndPrepDataForCES(countryAbbrev, energyType)
  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
  if (!(haveDataSF(countryAbbrev, energyType))){
    # If we don't have data for this combination of countryAbbrev and energyType, 
    # return a column of NAs if the above conditions have been met.
    nRows <- 21 # All of these countries need 21 rows.
    df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
    colnames(df) <- "pred"
    return(df)
  }
  model <- cesModel(countryAbbrev, energyType)
  pred <- fitted(model)
  df <- data.frame(pred)
  # Pad with rows as necessary
  df <- padRows(countryAbbrev, df)
  return(df)
}

#########################
# Takes the CES fitted models and creates a single column of predicted GDP values
# that corresponds, row for row, with the AllData.txt file.
##
cesPredictionsColumn <- function(energyType){
  out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions, energyType=energyType))
  colnames(out) <- c(paste("predGDP", energyType, sep=""))
  return(out)
}

@@

>>>>

#########################
# Takes the CES fitted models and creates per-country predictions for them.
# Returns a data.frame with the predictions.
# If energyType is not specified, the CES model without energy will be used.
##
cesPredictions <- function(countryAbbrev, energyType){
  if (missing(energyType)){
    model <- cesModel(countryAbbrev)
  } else {
    # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
    if (!(haveDataSF(countryAbbrev, energyType))){
      # If we don't have data for this combination of countryAbbrev and energyType, 
      # return a column of NAs if the above conditions have been met.
      nRows <- 21 # All of these countries need 21 rows.
      df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
      colnames(df) <- "pred"
      return(df)
    }
    model <- cesModel(countryAbbrev, energyType)
  }
  pred <- fitted(model)
  df <- data.frame(pred)
  # Pad with rows as necessary
  df <- padRows(countryAbbrev, df)
  return(df)
}

#########################
# Takes the CES fitted models and creates a single column of predicted GDP values
# that corresponds, row for row, with the AllData.txt file.
# If energyType is not specified, the CES model without energy will be used for the predictions.
##
cesPredictionsColumn <- function(energyType){
  if (missing(energyType)){
    out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions))      
    colnames(out) <- "predGDP"
  } else {
    out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions, energyType=energyType))  
    colnames(out) <- c(paste("predGDP", energyType, sep=""))
  }
  return(out)
}

@@

  predictions <- cesPredictionsColumn() #Predictions from CES without energy

### 2013-04-11 EconGrowth.Rnw
Now including CES without energy predictions in the CES lattice graph.

modelUS <- cesModel("US")
print(summary(modelUS))

>>>>

# print("US")
# print(summary(cesModel("US")))
# print("UK")
# print(summary(cesModel("UK")))
# print("JP")
# print(summary(cesModel("JP")))
# print("CN")
# print(summary(cesModel("CN")))
# print("ZA")
# print(summary(cesModel("ZA")))
# print("SA")
# print(summary(cesModel("SA")))
# print("IR")
# print(summary(cesModel("IR")))
# print("TZ")
# print(summary(cesModel("TZ")))
# print("ZM")
# print(summary(cesModel("ZM")))

# print(cesPredictionsColumn("Q"))
# print(cesPredictionsColumn())

# createCESLatticeGraph()
